---
title: "caterpillar_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{caterpillar_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
**caterpillar** is a package that enables you to perform various helpful functions to
caterpillar performance data.

Load the package.
```{r setup}
library(caterpillar)
```
Load the associated data (**caterpillar_survival**).
```{r}
data("caterpillar_survival")
```
You can use **avg_mass** to find the average mass change of a single caterpillar in a container across 2 to 3 given days.
```{r}
avg_mass(caterpillar_survival$alive_1, caterpillar_survival$mass_1, caterpillar_survival$alive_2, caterpillar_survival$mass_2)
```
You can use **avg_survival** to find the avergae survival of a given container across 2 or 3 stress exposures. 
```{r}
avg_survival(caterpillar_survival$alive_1, caterpillar_survival$alive_2)
```
You can use **development_time** to find the average number of days between instars across 2 to 4 instars. 
```{r}
development_time(caterpillar_survival$hatch_date, caterpillar_survival$instar2, caterpillar_survival$instar3)
```

Have fun!
